---
title: "Details Demo"
---

## Example 1

This example shows the use of the `dtext` shortcode to quickly create a details block containing text. The default summary text of "Details" is used and the details block is closed until opened.

### Syntax
`{{{< dtext "This is details text." >}}}`

### Output
{{< dtext "This is details text." >}}

## Example 2

This example shows the use of the `summary` argument to control the summary text.

### Syntax
`{{{< dtext "This is details text." summary="Hint" >}}}`

### Output

{{< dtext "This is details text." summary="Hint" >}}

## Example 3

This example shows the use of the `open` flag to make the details block open until closed.

### Syntax
`{{{< dtext "This is details text that is visible by default." summary="Hint" open >}}}`

### Output

{{< dtext "This is details text that is visible by default." summary="Hint" open >}}

## Example 4

This example shows the use of the `dstart` and `dstop` shortcodes to create a more flexible details block containing markdown as well as an executed code chunk.

### Syntax

````md
{{{< dstart summary="Answer Key" >}}}

**Here is some markdown**

```{{r}}
# And here is an R code chunk
plot(iris$Sepal.Length, iris$Sepal.Width)
```

{{{< dstop >}}}
````

### Output

{{< dstart summary="Answer Key" >}}

**Here is some markdown**

```{r}
# And here is an R code chunk
plot(iris$Sepal.Length, iris$Sepal.Width)
```

{{< dstop >}}

## Example 5

This example shows that the `open` flag works with the `dstart` shortcode too.

### Syntax

````md
{{{< dstart summary="Answer Key" open >}}}

**Here is some markdown**

```{{r}}
# And here is an R code chunk
plot(iris$Sepal.Length, iris$Sepal.Width)
```

{{{< dstop >}}}
````

### Output

{{< dstart summary="Answer Key" open >}}

**Here is some markdown**

```{r}
# And here is an R code chunk
plot(iris$Sepal.Length, iris$Sepal.Width)
```

{{< dstop >}}
